---
title: "Data Exploration"
author: Shun CHI
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(feather)
library(lubridate)
```

## Data wrangling

```{r}
stock_all <- read_feather("../data/stock_data.feather")
glimpse(stock_all)
```

```{r}
colum_list_to_keep <- c("Symbol", "Name", "MarketCap", "Sector", "industry", "Date", "Median_Quote", "Lower_Quote", "Upper_Quote", "Revenues", "Revenue_Growth", "Profit_Margin", "EPS", "Debt_to_Equity_Ratio","Net_Income", "Shareholders_Equity", "Cash_per_Share", "Book_Value_per_Share")

stock <- stock_all %>% 
        select(colum_list_to_keep)

stock$Sector <- factor(stock$Sector)
stock$industry <- factor(stock$industry)
stock$Symbol <- factor(stock$Symbol)

stock <- mutate(stock, Year = year(Date))


glimpse(stock)
```

## Visulization

```{r}
stock %>% filter( Year == 2016 ) %>% 
        ggplot(aes(y = MarketCap, x = Sector))+
        geom_jitter(size = 1, alpha = 0.3)+
        geom_violin(fill = "blue", alpha = 0.3)+
        theme(axis.text.x = element_text(angle = 45, hjust = 1))+
        scale_y_log10("Market Capitalization", breaks = c(1,10,100)*10000000000)
```


> For instance, an investor who is looking to buy undervalued stocks might select one with a low price-to-earnings ratio. The implicit hope is that the price would rise such that its price-to-earnings ratio will rebound to a level more in line with its peers. But what Kok et al. found is that the opposite is more likely to happen — the price-to-earnings ratio will return to normal levels, but only because the earnings in the denominator fell.

```{r}
stock %>% ggplot(aes(y = Median_Quote, x = Date, group = Symbol))+
        geom_line(alpha = 0.1)+
        scale_y_log10()
```
```{r}
 stock_new <- stock %>% group_by(Symbol) %>% mutate(PriceDiff = c(-diff(Median_Quote), NA_real_)/Median_Quote)
 stock_new %>%
        ggplot(aes(y = PriceDiff, x = Revenue_Growth ))+
        geom_hex(bins = 100)+
        scale_x_continuous(limits = c(-1 , 2))+
        scale_y_continuous(limits = c(-2, 1))+
        scale_fill_distiller(palette = "Spectral")
```


```{r}
# stock_new <- stock %>% group_by(Symbol) %>% mutate(PriceDiff = c(-diff(Median_Quote), NA_real_)/Median_Quote)
 stock_new %>%
        ggplot(aes(y = PriceDiff, x = Profit_Margin ))+
        geom_hex(bins = 100)+
        scale_x_continuous(limits = c(-1 , 1))+
        scale_y_continuous(limits = c(-1, 1))+
        scale_fill_distiller(palette = "Spectral")
```

```{r}
# stock_new <- stock %>% group_by(Symbol) %>% mutate(PriceDiff = c(-diff(Median_Quote), NA_real_)/Median_Quote)
 stock_new %>%
        ggplot(aes(y = PriceDiff, x = MarketCap ))+
        geom_hex(bins = 100)+
        scale_x_log10(breaks = c(1,10 , 100)*10000000000)+
        scale_y_continuous(limits = c(-1, 1))+
        scale_fill_distiller(palette = "Spectral")
```




```{r}
# stock_new <- stock %>% group_by(Symbol) %>% mutate(PriceDiff = c(-diff(Median_Quote), NA_real_)/Median_Quote)
 stock_new %>%
        ggplot(aes(y = PriceDiff, x = Median_Quote/EPS ))+
        geom_hex(bins = 100)+
        scale_x_continuous(limits = c(-100 , 100))+
        scale_y_continuous(limits = c(-1, 1))+
        scale_fill_distiller(palette = "Spectral")
```