---
title: "Data Exploration"
author: Shun CHI
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(feather)
library(lubridate)
```

## Data wrangling

Select financial indicators for analysis.

```{r}
stock_all <- read_csv("../data/stock_data_clean.csv")
glimpse(stock_all)
```

```{r}
colum_list_to_keep <- c("Symbol", "Name", "MarketCap", "Sector", "Industry", "Date", "Median_Quote", "Median_Q_Increase", "UpLow_Q_Var90", "Lower_Quote", "Upper_Quote", "Revenues", "Revenue_Growth", "Profit_Margin", "Debt_to_Equity_Ratio","Net_Income", "Shareholders_Equity", "Total_Liabilities", "Cash_per_Share", "EPS", "Book_Value_per_Share")

stock <- stock_all %>% 
        select(colum_list_to_keep)

stock$Sector <- factor(stock$Sector)
stock$industry <- factor(stock$Industry)
stock$Symbol <- factor(stock$Symbol)

stock <- mutate(stock, Year = year(Date))

glimpse(stock)
```



```{r}
stock_selected <- stock %>% mutate(PEratio = Median_Quote/EPS, ROE = Net_Income/Shareholders_Equity, DEratio = Debt_to_Equity_Ratio) %>% select(Symbol, Name, MarketCap, Sector, Industry, Year, Date, Median_Quote, Median_Q_Increase, ROE, DEratio, Profit_Margin, PEratio, Revenue_Growth)

FiveYearMean <- function(x){
  len <- length(x)
  means <- rep(NA_real_, len)
  for (i in 1:(len-4)){
    means[i] <- mean(x[i:(i+4)])
  }
  return(means)
}


stock_selected <- 
  stock_selected %>% 
  group_by(Symbol) %>% 
  mutate(ROE_5Y = FiveYearMean(ROE),
         DEratio_5Y = FiveYearMean(DEratio),
         Profit_Margin_5Y = FiveYearMean(Profit_Margin)
         )
```


## Visulization

First exploration of the dataset

```{r}
stock_selected %>% filter( Year == 2016 ) %>% 
        ggplot(aes(y = MarketCap, x = Sector))+
        geom_jitter(size = 1, alpha = 0.3)+
        geom_violin(fill = "blue", alpha = 0.3)+
        theme(axis.text.x = element_text(angle = 45, hjust = 1))+
        scale_y_log10("Market Capitalization", breaks = c(1,10,100)*10000000000)
```



Visualized stock growth (percentage to last year) vs time. Overall, the prices grow in the last 9 year.

```{r}
stock %>% ggplot(aes(y = Median_Quote, x = Date, group = Symbol))+
        geom_line(alpha = 0.1)+
        scale_y_log10()
```

```{r}
stock_selected %>% ggplot(aes(ROE_N))+geom_histogram()+scale_x_continuous(limits = c(-1, 1))
```


Visualized stock growth (percentage to last year) vs revenue growth rate

```{r}
 stock_selected %>%
        ggplot(aes(y = Median_Q_Increase/Median_Quote, x = Revenue_Growth))+
        geom_hex(bins = 50)+
        scale_x_continuous(limits = c(-1 , 2))+
        scale_y_continuous(limits = c(-2, 1))+
        scale_fill_distiller(palette = "Spectral")
```


Visualized stock growth (percentage to last year) vs profit margin

```{r}
# stock_new <- stock %>% group_by(Symbol) %>% mutate(PriceDiff = c(-diff(Median_Quote), NA_real_)/Median_Quote)
 stock_selected %>%
        ggplot(aes(y =Median_Q_Increase/Median_Quote,  x = Profit_Margin ))+
        geom_hex(bins = 50)+
        scale_x_continuous(limits = c(-1 , 1))+
        scale_y_continuous(limits = c(-1, 1))+
        scale_fill_distiller(palette = "Spectral")
```

```{r}
# stock_new <- stock %>% group_by(Symbol) %>% mutate(PriceDiff = c(-diff(Median_Quote), NA_real_)/Median_Quote)
 stock_selected %>%
        ggplot(aes(y =Median_Q_Increase/Median_Quote,  x = Profit_Margin_5Y ))+
        geom_hex(bins = 50)+
        scale_x_continuous(limits = c(-1 , 1))+
        scale_y_continuous(limits = c(-1, 1))+
        scale_fill_distiller(palette = "Spectral")
```


Visualized stock growth (percentage to last year) vs different market cap size.

```{r}
# stock_new <- stock %>% group_by(Symbol) %>% mutate(PriceDiff = c(-diff(Median_Quote), NA_real_)/Median_Quote)
 stock_selected %>%
        ggplot(aes(y = Median_Q_Increase/Median_Quote, x = MarketCap ))+
        geom_hex(bins = 50)+
        scale_x_log10(breaks = c(1,10 , 100)*10000000000)+
        scale_y_continuous(limits = c(-1, 1))+
        scale_fill_distiller(palette = "Spectral")
```


Visualized stock growth (percentage to last year) vs PE ratio

```{r}
# stock_new <- stock %>% group_by(Symbol) %>% mutate(PriceDiff = c(-diff(Median_Quote), NA_real_)/Median_Quote)
 stock_selected %>%
        ggplot(aes(y = Median_Q_Increase/Median_Quote, x = PEratio ))+
        geom_hex(bins = 50)+
        scale_x_continuous(limits = c(-100 , 100))+
        scale_y_continuous(limits = c(-1, 1))+
        scale_fill_distiller(palette = "Spectral")
```

Visualized stock growth (percentage to last year) vs debet/equity ratio

```{r}
# stock_new <- stock %>% group_by(Symbol) %>% mutate(PriceDiff = c(-diff(Median_Quote), NA_real_)/Median_Quote)
 stock_selected %>%
        ggplot(aes(y = Median_Q_Increase/Median_Quote, x = DEratio ))+
        geom_hex(bins = 50)+
        scale_x_continuous(limits = c(-10 , 10))+
        scale_y_continuous(limits = c(-1, 1))+
        scale_fill_distiller(palette = "Spectral")
```



Visualized stock growth (percentage to last year) vs debet/equity ratio

```{r}
# stock_new <- stock %>% group_by(Symbol) %>% mutate(PriceDiff = c(-diff(Median_Quote), NA_real_)/Median_Quote)
 stock_selected %>%
        ggplot(aes(y = Median_Q_Increase/Median_Quote, x = ROE_N ))+
        geom_hex(bins = 30)+
        scale_x_continuous(limits = c(-5 , 5))+
        scale_y_continuous(limits = c(-1, 1))+
        scale_fill_distiller(palette = "Spectral")
```


Things to check

> For instance, an investor who is looking to buy undervalued stocks might select one with a low price-to-earnings ratio. The implicit hope is that the price would rise such that its price-to-earnings ratio will rebound to a level more in line with its peers. But what Kok et al. found is that the opposite is more likely to happen — the price-to-earnings ratio will return to normal levels, but only because the earnings in the denominator fell.